Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/related_work.tex
f'ed around with related work

While there has been much work in multi-label classification of text and
text modeling in general, we focus here on topic modeling approaches.
Latent Dirichlet allocation (LDA) is a generative probabilistic model which
represents documents as a mixed-membership bag of word. Each document is
represented as a collection of words, generated from a set of topic assignments
(one for each word), where each topic assignment is drawn from a distribution
over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
\cite{Blei2003} augmented with per-document labeling, often taking the form of
a single numerical or categorical label. Examples of labels include rating
associated with an online  eview, grades for an essay, and number of times a
webpage is linked. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.

@@

Other models that incorporate LDA and supervision include
LabeledLDA\citep{Ramage2009}, DiscLDA\citep{DiscLDA}, and other models applied to 
computer vision and document networks\citep{wangbleifeifei08,RelationalLDA}. 
These models, however, do not implement contraints on the label space.

In other work, researchers have classified documents in a hierarchy with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.

>>>>

In this work we extend supervised latent Dirichlet allocation (sLDA) \cite{BleiMcAuliffe2008} to take advantage of hierarchical supervision.  sLDA is latent Dirichlet allocation (LDA) \cite{Blei2003} augmented with per document ``supervision'';  often taking the form of a single numerical or categorical label. More generally this supervision is just extra per-document data;  for instance its quality or relevance (e.g.~online review scores), marks given to written work (e.g.~essay grades), or the number of times a web page is linked.  These labels are usually generatively modeled as a conditional draw from some distribution that depends on each document-specific topic mixture.  It has been demonstrated that the signal provided by such supervision can result in better, task-specific document models and can also lead to good label prediction for out-of-sample data \cite{BleiMcAuliffe2008}.  It also has been demonstrated that sLDA has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.  sLDA can be applied to data of the type we consider in this paper; however, doing so requires ignoring the hierarchical dependencies amongst the labels.  In Section~\ref{sec:experiments} we constrast HSLDA with sLDA applied in this way.

%While there has been much work in multi-label classification of text and
%text modeling in general, we focus here on topic modeling approaches.
%Latent Dirichlet allocation (LDA) is a generative probabilistic model which
%represents documents as a mixed-membership bag of word. Each document is
%represented as a collection of words, generated from a set of topic assignments
%(one for each word), where each topic assignment is drawn from a distribution
%over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
%\cite{Blei2003} augmented with per-document labeling, often taking the form of
%a single numerical or categorical label. Examples of labels include ratings
%associated with online reviews, grades for essays, and the number of times a
%webpage is linked. This approach has been shown to outperform both LASSO
%(L1 regularized least squares regression) and LDA followed by least
%squares regression~\cite{BleiMcAuliffe2008}.

@@

Other models that incorporate LDA and supervision include
LabeledLDA\citep{Ramage2009} and DiscLDA\citep{DiscLDA}.  Various applications of these models to 
computer vision and document networks have been explored \citep{wangbleifeifei08,RelationalLDA} . 
None of these models, however, leverage dependency structure in the label space.

In other work, researchers have classified documents into a hierarchy (a closely related task) with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces, and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.
